Assessing Virulence by MCG

### 2017-07-11 doc/RMD/MCG-virulence.Rmd
export table from MCG-virulence analysis

```{r anova, fig.width = 4, fig.height = 8}
ANOVA <- aov(Severity ~ MCG, data = top_mcg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA), las = 2)
agricolae::HSD.test(ANOVA, "MCG")$groups
```

>>>>

```{r anova, fig.width = 4, fig.height = 8}
ANOVA <- aov(Severity ~ MCG, data = top_mcg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "MCG", alpha = 0.05)$groups
readr::write_csv(grps, path = "results/tables/MCG-aggressiveness.csv", col_names = TRUE)

grps %>% 
  dplyr::rename(MCG = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.05, 0.3, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 31)
```
